---
title: "Homework 2"
author: "Kevin Akers"
#date: "September 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(swirl)
library(dplyr)
library(readr)
library(tidyr)
```

## Problem 4
The first and most obvious benefit of using a version control system is that it allows a user to store and have instant access to all the versions of a particular project. This in turn allows one to return to any previous state if necessary. I believe this is helpful both in the classroom and on the job.

##Problem 5
###A
I had a dozen problems trying to import the data directly from the URL, so I had to input it manually in vectors. Then I made a data.frame from the vectors and took the transpose so that the rows became the observations and the columns became the variables.
```{r, echo=TRUE}
v1 <- c(4.3, 4.9, 3.3, 5.3, 4.4)
v2 <- c(4.3, 4.5, 4.0, 5.5, 3.3)
v3 <- c(4.1, 5.3, 3.4, 5.7, 4.7)
v4 <- c(6.0, 5.3, 4.5, 5.9, 4.7)
v5 <- c(4.9, 6.3, 4.2, 5.5, 4.9)
v6 <- c(6.0, 5.9, 4.7, 6.3, 4.6)
v7 <- c(2.4, 2.5, 2.3, 3.1, 2.4)
v8 <- c(3.9, 3.0, 2.8, 2.7, 1.3)
v9 <- c(1.9, 3.9, 2.6, 4.6, 2.2)
v10 <- c(7.4, 8.2, 6.4, 6.8, 6.0)
v11 <- c(7.1, 7.9, 5.9, 7.3, 6.1)
v12 <- c(6.4, 7.1, 6.9, 7.0, 6.7)
v13 <- c(5.7, 6.3, 5.4, 6.1, 5.9)
v14 <- c(5.8, 5.7, 5.4, 6.2, 6.5)
v15 <- c(5.8, 6.0, 6.1, 7.0, 4.9)
v16 <- c(2.2, 2.4, 1.7, 3.4, 1.7)
v17 <- c(3.0, 1.8, 2.1, 4.0, 1.7)
v18 <- c(2.1, 3.3, 1.1, 3.3, 2.1)
v19 <- c(1.2, 1.5, 1.2, 0.9, 0.7)
v20 <- c(1.3, 2.4, 0.8, 1.2, 1.3)
v21 <- c(0.9, 3.1, 1.1, 1.9, 1.6)
v22 <- c(4.2, 4.8, 4.5, 4.6, 3.2)
v23 <- c(3.0, 4.5, 4.7, 4.9, 4.6)
v24 <- c(4.8, 4.8, 4.7, 4.8, 4.3)
v25 <- c(8.0, 8.6, 9.0, 9.4, 8.8)
v26 <- c(9.0, 7.7, 6.7, 9.0, 7.9)
v27 <- c(8.9, 9.2, 8.1, 9.1, 7.6)
v28 <- c(5.0, 4.8, 3.9, 5.5, 3.8)
v29 <- c(5.4, 5.0, 3.4, 4.9, 4.6)
v30 <- c(2.8, 5.2, 4.1, 3.9, 5.5)
sensory <- data.frame(v1, v2, v3, v4, v5, v6, v7, v8, v9, v10, v11, v12, v13, v14, v15, v16, v17, v18, v19, v20, v21, v22, v23, v24, v25, v26, v27, v28, v29, v30)
sensory <- t(sensory)
colnames(sensory) <- c("Op1", "Op2", "Op3", "Op4", "Op5")
rownames(sensory) <- c(1,1,1,2,2,2,3,3,3,4,4,4,5,5,5,6,6,6,7,7,7,8,8,8,9,9,9,10,10,10)
sensory
summary(sensory)
```
###B
I /finally/ figured out how to read in the file correctly. I'll be the first to admit that my programming background is not that strong and that's it's been a while since I've done any programming at all. I know it doesn't represent my best work, but I'm going to leave part (a) the same above, just to illustrate my learning process.
```{r, echo = TRUE}
jump <- read.table("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/LongJumpData.dat", sep = " ", fill = TRUE, skip = 1)
jump <- data.frame(stack(jump, c("V1", "V3", "V5", "V7")), stack(jump, c("V2", "V4", "V6", "V8")))
jump <- jump[,-c(2,4)]
jump <- na.omit(jump)
colnames(jump) <- c("Year", "Long Jump")
jump$Year <- jump$Year + 1900 
jump
summary(jump)
```

###C
Same process as (b).
```{r, echo = TRUE}
brain <- read.table("https://www2.isye.gatech.edu/~jeffwu/wuhamadabook/data/BrainandBodyWeight.dat", sep = " ", fill = TRUE, skip = 1)
brain <- data.frame(stack(brain, c("V1", "V3", "V5")), stack(brain, c("V2", "V4", "V6")))
brain <-brain[,-c(2,4)]
brain <- na.omit(brain)
colnames(brain) <- c(" Body Weight", "Brain Weight")
brain
summary(brain)
```

###D
I had to return to manual entry again; couldn't load the data properly.
```{r, echo = TRUE}
variety <- rep(c("Ife", "Pusa"), each = 9)
density <- rep(c(10000,10000,10000,20000,20000,20000,30000,30000,30000), times = 2)
yield <- c(16.1,15.3,17.5,16.6,19.2,18.5,20.8,18.0,21.0,8.1,8.6,10.1,12.7,13.7,11.5,14.4,15.4,13.7)
tomato <- data.frame(variety, density, yield)
tomato
summary(tomato)
```

##Problem 6
I started by selecting the appropriate variables and removing the entries that were missing data.
```{r, echo=FALSE}
.datapath <- file.path(path.package('swirl'), 'Courses',
'R_Programming_E', 'Looking_at_Data',
'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")
# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
'Foliage_Color', 'pH_Min', 'pH_Max',
'Precip_Min', 'Precip_Max',
'Shade_Tolerance', 'Temp_Min_F')
```
```{r}
plants2 <- select(plants, pH_Min, pH_Max)
plants3 <- filter(plants2, !is.na(pH_Min), !is.na(pH_Max))
```
Then I ran the analysis.
```{r}
simple.fit <- lm(pH_Min~pH_Max, plants3)
summary(simple.fit)
```