---
title: "Homework 2"
author: "Kevin Akers"
#date: "September 4, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(swirl)
library(dplyr)
```

## Problem 4
The first and most obvious benefit of using a version control system is that it allows a user to store and have instant access to all the versions of a particular project. This in turn allows one to return to any previous state if necessary. I believe this is helpful both in the classroom and on the job.

##Problem 5
I completely ran out of time while working on this assignment and take full responsibility for it.

##Problem 6
I started by selecting the appropriate variables and removing the entries that were missing data.
```{r, echo=FALSE}
.datapath <- file.path(path.package('swirl'), 'Courses',
'R_Programming_E', 'Looking_at_Data',
'plant-data.txt')
# Read in data
plants <- read.csv(.datapath, strip.white=TRUE, na.strings="")
# Remove annoying columns
.cols2rm <- c('Accepted.Symbol', 'Synonym.Symbol')
plants <- plants[, !(names(plants) %in% .cols2rm)]
# Make names pretty
names(plants) <- c('Scientific_Name', 'Duration', 'Active_Growth_Period',
'Foliage_Color', 'pH_Min', 'pH_Max',
'Precip_Min', 'Precip_Max',
'Shade_Tolerance', 'Temp_Min_F')
```
```{r}
plants2 <- select(plants, pH_Min, pH_Max)
plants3 <- filter(plants2, !is.na(pH_Min), !is.na(pH_Max))
```
Then I ran the analysis.
```{r}
simple.fit <- lm(pH_Min~pH_Max, plants3)
summary(simple.fit)
```